Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2019-06-11 tex/VHzQ.tex
general update

\begin{figure}
  \centering
  \includegraphics[width=8.5cm]
  {/cos_pc19a_npr/programs/quasars/highest_z/light_curves/MIR_LCs/NEOWISER_LC_histogramlog_20180827.png}
  \vspace{-16pt}
  \caption[]
  {Histogram showing the total number of exposures for each detected VH$z$Q
    from the full combination of ALLWISE, NEOWISE and NEOWISE-R.} 
  \label{fig:MIR_LC_epochs}
\end{figure}
\subsection{Variability}
VH$z$Qs, if accreting at, or above the Eddington Limit, might well
have have large values of changing mass accretion rate, $\ddot{m}_{\rm
accr}$. A consequence of this would be that these quasars exhibit signs
of variability, most likely showing up in their UV/optical rest-frame
spectra. We look for evidence of this variability signature in the NIR
and MIR light-curves of the VH$z$Qs.

Quasars are known to have dramatically changing Balmer lines, especially 
H$\beta$ \citep[e.g.,][]{LaMassa2015, Ruan2016, Runnoe2016, Macleod2016,
Gezari2017, Runco2016, Yang2017, Assef2018, Stern2018, Wang2018,
Ross2018, MacLeod2019, Graham2019}.
As a guide, 
What is less well understood is the temporal behvaiour of the metal lines, in particular \civ and \mgii. 
\civ enters the
$Y$-band at redshift $z$=5.32 and exits at $z$=5.99, and enters the
$J$-band at redshift $z=6.55$ and exits at $z$=7.57. \mgii enters the
$H$-band at redshift $z=4.33$ and exits at $z=5.37$ and enters the
$K$-band at redshift $z=6.25$ and exits at $7.50$.

Using the extended datasets described in Section~\ref{sec:NIR_data} and~\ref{sec:NIR_SQL}, we

\begin{figure}
  \includegraphics[width=8.5cm]
  {/cos_pc19a_npr/programs/quasars/highest_z/light_curves/MIR_LCs/three_MIR_LC_egs_20180827.pdf}
  \centering
  \caption[]
  {Here we show the MIR NEOWISE-R for J0100+2802 \citep{Wu2015}, J0224-4711 and  J1626+2751. 
    Red points are the W1 band; cyan points the W2 band.} 
  \label{fig::MIR_LC_3egs}
\end{figure}

@@

At least 8 original observations across at least 30 days in either WSA
or VSA per band, calibrated flux greater than zero over the whole
time, and the error on the average flux is 8 times lower than this.
%%
Then a requirement of SNR$>3$ per `average' epoch, where `average epoch' is then dependent on the averaging timescales (which as we see can vary).

>>>>

\begin{figure}
  \centering
  \includegraphics[width=8.5cm]
  {../light_curves/MIR_LCs/NEOWISER_LC_histogramlog_20180827.png}
  \vspace{-16pt}
  \caption[]
  {Histogram showing the total number of exposures for each detected VH$z$Q
    from the full combination of ALLWISE, NEOWISE and NEOWISE-R.} 
  \label{fig:MIR_LC_epochs}
\end{figure}
\subsection{Variability}
VH$z$Qs, if accreting at, or above the Eddington Limit, might well have have large values of changing mass accretion rate, $\ddot{m}_{\rm accr}$. A consequence of this would be that these quasars exhibit signs of variability, most likely showing up in their UV/optical rest-frame spectra. We look for evidence of this variability signature in the NIR and MIR light-curves of the VH$z$Qs.

Quasars are known to have dramatically changing Balmer lines, especially H$\beta$ \citep[e.g.,][]{LaMassa2015, Ruan2016, Runnoe2016, Macleod2016, Gezari2017, Runco2016, Yang2017, Assef2018, Stern2018, Wang2018, Ross2018, MacLeod2019, Graham2019}. As a guide, we note that H$\alpha$ is redshifted to 3.94$\mu$ (i.e. W1) at $z=5.00$ and 5.57$\mu$m, which is between the W2 and W3-bands at $z=7.50$. 
H$\beta$ is redshifted to 2.92$\mu$m, which is the blue edge of W1, at $z=5.00$ and 
4.13$\mu$m at $z=7.50$. 
%%
Less well understood is the temporal behvaiour of the metal lines, in particular \civ and \mgii. 
\civ enters the
$Y$-band at redshift $z$=5.32 and exits at $z$=5.99, and enters the
$J$-band at redshift $z=6.55$ and exits at $z$=7.57. \mgii enters the
$H$-band at redshift $z=4.33$ and exits at $z=5.37$ and enters the
$K$-band at redshift $z=6.25$ and exits at $7.50$.

\begin{figure}
  \includegraphics[width=8.5cm]
  {/cos_pc19a_npr/programs/quasars/highest_z/light_curves/MIR_LCs/three_MIR_LC_egs_20180827.pdf}
  \centering
  \caption[]
  {Here we show the MIR NEOWISE-R for J0100+2802 \citep{Wu2015}, J0224-4711 and  J1626+2751. 
    Red points are the W1 band; cyan points the W2 band.} 
  \label{fig:MIR_LC_3egs}
\end{figure}

@@

Using the extended datasets described in Section~\ref{sec:NIR_data}, we find there are 27 WFCAM and 16 VISTA objects with at least 8 measurements observed with durations over 30 days, in at least one filter. 4 objects are in common to both, so this sample of 39 is our starting point for variability investigations. The four objects in common are: CFHQS J0216-4555; SDSS J0959+0227; SDSS J1000+0234; VIK J1148+0056. 
%% is SDSSJ0958+3524 special at all??

At least 8 original observations across at least 30 days in either WSA or VSA per band, calibrated flux greater than zero over the whole time, and the error on the average flux is 8 times lower than this. Then a requirement of SNR$>3$ per `average' epoch, where `average epoch' is then dependent on the averaging timescales (which as we see can vary).
